### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@ba848f26beb3af983f349ea50656cbd0b13f830e 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e0c5e91694a0aa699b3e2c6a62380c918777d40d 🚀

\textbf{TK final paragraph} \textgreater{} Set up the key research
challenges in this field so that the reader understands where your
thesis fits in. \textgreater{} Finish the introduction with a short
summary of what you will do across your chapters. This is the bridging
paragraph to your chapters.

The primary reserach challenges this thesis addresses: how do we design
ecological samples? Data assimilation pipeline. How do we propgate
uncertainty from these samples into forecasts? More details on pipeline
flow

@@

The first result is to compute a null expectation of the probability of
an interaction false-negative as a function number of total observations
of individuals of \emph{any species}. This is done by simulating the
process of observation, where the probability of observing a given
species is its relative abundance. We use a log-normal distribution of
relative abundance (Hubbell 2001) and simulating the process of
observation on food-webs generated using the niche model (Williams \&
Martinez 2000) with connectance parameterized by the flexible-links
model (MacDonald \emph{et al.} 2020).

An example of this relation for networks with varying spceies richness
is shown in fig.~\ref{fig:fnr}.

@@

@@

@@

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

@@

This chapter is mostly complete. The only remaining work is the
implementation of simulated annealing optimization process.

@@

Here we show the in-progress work on the prerequisites for the analysis
outlined above: phylogenies for both plant and bee species
(fig.~\ref{fig:phylo}) and species distribution models for all species
(an example shown in fig.~\ref{fig:example_sdm}).

@@

I have a phylogeny and SDMs for all the species. Waiting on data
agreement with RMBL.

@@

@@

@@

@@

\begin{figure}
\centering
\includegraphics{./figures/foodwebtraj.png}
\caption{Sample output of simulated food web dynamics from
MetacommunityDynamics.jl}
\end{figure}

@@

\hypertarget{discussion-1}{%
\section{Discussion}\label{discussion-1}}

>>>>

The primary research challenges this thesis addresses: how do we design
ecological samples to? How do we build the software infrastructure to
assimilate data from a variety of sources? How do we propagate
uncertainty from data to forecasts? The flow of chapters follows the
flow in fig.~\ref{fig:thesis} (left), from data collection via a
monitoring network, to forecasting an essential biodiversity variable
(EBV), to optimizing mitigation strategy based on constraints. In
chapter one, we discuss how simulation can aid in the design of
ecological samples and monitoring network design. In chapter two we use
data to forecast the uncoupling of a plant-pollinator network. In
chapter three, we apply simulation methods in landscape ecology to
optimize corridor placement with respect maximize the
time-until-extinction of a metapopulation. The fourth and final chapter
is the software (\emph{MetacommunityDynamics.jl}) which enables the rest
of the dissertation.

@@

The first result is to compute a null expectation of the probability of
an interaction false-negative as a function number of total observations
of individuals of \emph{any species}. This is done by simulating the
process of observation, where the probability of observing a given
species is its relative abundance. We use a log-normal distribution of
relative abundance (Hubbell 2001) and simulating the process of
observation on food-webs generated using the niche model (Williams \&
Martinez 2000) with connectance parameterized by the flexible-links
model (MacDonald \emph{et al.} 2020). An example of this relation for
networks with varying spceies richness is shown in fig.~\ref{fig:fnr}.

@@

The first major result is using the simulation of the observation
process described above to generate expectations of interaction
false-negative rate (FNR) as a function of total number of observations,
with the goal being for this estimate to be used as correction for
detection error when fitting an interaction prediction model. This
relationship varies with the total richness of the metaweb
fig.~\ref{fig:fnr}.

@@

The second major result is that we analytically show that the this
simulated observation model, by assuming that there is no correlation
between observing two species given that they interaction, actually
underpredicts the realized false-negative interaction rate. We then
demonstrate that this association exists in two empirical systems
fig.~\ref{fig:posassoc}.

@@

@@

This chapter is mostly complete. The only remaining work is the
implementation of simulated annealing optimization process. This will be
done by using a proposal function which takes a set of coordinates in
space and proposes a new location for each point based on a
distance-decaying kernel.

@@

Here we show the in-progress results, which are the prerequisites for
the analysis outlined above: phylogenies for both plant and bee species
(fig.~\ref{fig:phylo}) and species distribution models for all species
(an example shown in fig.~\ref{fig:example_sdm}).

@@

At the moment, we have derived phylogenies and SDMs for all the species
present in the Colorado GBIF metaweb. I've also been exploring the data
available from Julian Resasco. The primary constraint on further
progress is that we are waiting on the finalization of a data sharing
agreement with RMBL.

@@

The current progress is that I have an algorithm for proposing landscape
modifications and a simple implementation of simulated annealing. The
only gap left is implementing Circuitscape estimation of resistance
surfaces.

@@

\hypertarget{objective-2}{%
\subsection{Objective}\label{objective-2}}

@@

\hypertarget{methods-3}{%
\subsection{Methods}\label{methods-3}}

@@

\hypertarget{results-3}{%
\subsection{Results}\label{results-3}}

Below (fig.~\ref{fig:foodwebtraj}) is a sample output of simulated
food-web dynamics for a metaweb of 100 species generated using the
minimum-potential-niche model with connectance \(C=0.05\) and
forbidden-link probability of \(0.5\). The dynamics change according to
a Lotka-Volttera functional response, dispersal (with dispersal distance
inverse proportional to trophic-level), linear mortality, and logistic
growth for any species at the producer trophic-level.

\begin{figure}
\hypertarget{fig:foodwebtraj}{%
\centering
\includegraphics{./figures/foodwebtraj.png}
\caption{Sample output of simulated food web dynamics from
MetacommunityDynamics.jl}\label{fig:foodwebtraj}
}
\end{figure}

\hypertarget{progress-3}{%
\subsection{Progress}\label{progress-3}}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}
